Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-05 Manuscript/manuscript.tex
Added basic information and sentences into section simulation details

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations. 
           Given concentrations adopt the form $C_{bulk}/C_{buffer}$. 
        }
\todo{Joe: to be filled-in. I'll generate it automatically from my Jupyter notebooks.}  
\label{IONsystems_conc}
\begin{tabular}{l c c r r r r }
  lipid/counter-ions &  KCl (mM)  &  NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules with the largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   &  \footnote{Simulation temperature}T (K)  \\
  \hline
    POPC:POPS (5:1)/K$^+$  & tba & tba & 60:12 & 9999 & 298  \\
    \hline
    POPC:POPS (5:1)/Na$^+$ & tba & tba & 60:12 & 9999 & 298  \\
    \hline
\end{tabular}
\end{table*}

General simulation setup.

Any specifics for simulations with aqueous cations.

Any specifics for simulations with anionic/cationinc surfactants/peptides. 
e.g. where the parameters for them came from.

>>>>

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations. 
           Given concentrations adopt the form $C_{bulk}/C_{buffer}$. 
        }
\todo{Joe: to be filled-in. I'll generate it automatically from my Jupyter notebooks.}  
\label{tbl:sim-list}
\begin{tabular}{l c c r r r r }
  lipid/counter-ions &  KCl (mM)  &  NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules with the largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   &  \footnote{Simulation temperature}T (K)  \\
  \hline
    POPC:POPS (5:1)/K$^+$  & tba & tba & 60:12 & 9999 & 298  \\
    \hline
    POPC:POPS (5:1)/Na$^+$ & tba & tba & 60:12 & 9999 & 298  \\
    \hline
\end{tabular}
\end{table*}

MD simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 2018). 
The simulation parameters used in this work are summarized in Table~\ref{tbl:mdpar}. 
A comprehensive list of simulaitons used in this work is in Table~\ref{tbl:sim-list}.

\begin{table}[tbp]
  \caption{Simulation parameters}
  \label{tbl:mdpar}
  \begin{tabular}{ll}
    simulation property & parameter   \\
    \hline
    time-step           & 2~fs         \\
    equilibration time  & tba~ns  \\
    total simulation time     & 1.5~$\mu$s  \\
    temperature         & 298~K       \\
    thermostat          & v-rescale  \cite{bussi07}   \\
    barostat            & Parrinello-Rahman, semi-isotropic \cite{parrinello81} \\
    long-range electrostatics & PME  \cite{darden93}  \\
    cut-off scheme      & Verlet \cite{Pall13}      \\
    Coulomb and VdW cut-off & 1.0~nm \\
    constraints         & LINCS, only hydrogen atoms \cite{hess97} \\
    constraints for water & SETTLE  \cite{miyamoto92} \\
    \hline
  \end{tabular}
\end{table}

For deposited trajectories and parameter files see 
Refs.~\citenum{TBA}.
\todo{Joe: Upload trajectories and add references here.}
